### 2020-06-21 design.tex
add eval

\section{System Design}
\label{sec-design}
As mentioned above, we designed merging layers in our network so that we can process the input images by performing convolution operations to each single image, and then merging them together. The merged data will be stacked with the feature maps of each single image before we perform the next layer of convolution on them. Each convolutional layer uses the same set of parameters for all the images, so that the same set of features are extracted from the images, and thus can be merged. The merging layers consists of simple calculations extracting either the most significant, or the mutual features of the images, the former preserving interesting findings while the latter filters out credible features from the redundancy of the input. The network pipeline consists of alternate layers of convolution and merging, and after each merging layer, the reliable information accumulates and more complex features can be extracted with their support. Furthermore, we frequently insert the original input images in each level of our pipeline, creating an unevenness in depth and reducing network complexity, because we discovered that this process guides the model to be loyal to the inputs, generating more truthful results and less artifacts.

@@

>>>>

\section{Design}
\label{sec-design}

\subsection{network design}

As mentioned above, we designed merging layers in our network so that we can process the input images by performing convolution operations to each single image, and then merging them together. The merged data will be stacked with the feature maps of each single image before we perform the next layer of convolution on them. Each convolutional layer uses the same set of parameters for all the images, so that the same set of features are extracted from the images, and thus can be merged. The merging layers consists of simple calculations extracting either the most significant, or the mutual features of the images, the former preserving interesting findings while the latter filters out credible features from the redundancy of the input. The network pipeline consists of alternate layers of convolution and merging, and after each merging layer, the reliable information accumulates and more complex features can be extracted with their support. Furthermore, we frequently insert the original input images in each level of our pipeline, creating an unevenness in depth and reducing network complexity, because we discovered that this process guides the model to be loyal to the inputs, generating more truthful results and less artifacts.

@@

\subsection{system design}

We implemented a holistic system for shoulder surfing, with the neural network as core, on a smartphone to verify the efficiency of our model. It iterates through the following steps: 
\begin{enumerate}

\item Input. Under guidance of the attacker, The smartphone will zoom in, take focus, and take 20 images with burst mode of the target screen. Note that the zoom in step is only for easier interaction and focusing, and to utilize the telephoto lenses and optical zoom, if avaliable, as digital zooming do not put in any extra data; On traditional phones with only digital zooming, the photo-taking will be with 1x zoom, and on phones with optical zooming, 5x to 10x zoom, depending on the optical zooming range. This way information on the images will be more compact and easier to comprehend by neural networks.

\item Alignment. The images are then aligned to mitigate the shifts between frames caused by hand tremor or movements from the lenses, as cameras with optical lenses will ocationally shift slightly across time due to the movements of its inner mechanism. Luckily, in our scenario the target is a glowing screen whose edges are easily distinguishable in most cases, and we use them as reference to align our images. The images are also spun to make the text horizontal in the process. The screen is cropped out and the rest of the image abandoned.

\item Adjustment. The lines of text(or stuff differing from the background color of the screen) will be carved out for processing, to reduce the workload of the network. The characters are normally around 10x10 pixels in the photos, and the carved segments will leave 2 pixels of padding on all sides to avoid mutilating the character; A certain amount of error is allowed, but if the size of the text is too small or too large, the neural network will not be able to extract features normally, so the images will be zoomed to the right size(and the zooming of step (1) will be adjusted accordingly).

\item Processing. As our network accepts only 9x9 patches, we will iteratively process all the overlapping 9x9 boxes among the input photo. For example, a 10x10 image will be four 9x9 patches, and a 11x11 image nine patches, etc(see fig.~\ref{fig-patches}. After carving a 9x9 patch at corresponding locations of each image, these patches are then processed by our multi-frame super resolution network, generating a single 36x36 image (4x upscaling). The input is RGB colored, while the output, as we are not interested in color, is black and white. When all patches are processed, their outputs are merged together. The overlapping pixels are thus processed: among all the outputs containing this pixel, we collect these values, remove outliers, and use their average as the result. In this way, we generate upscaled image segments of all the characters on the target screen, which are then inserted in one of the input images(roughly upscaled to encompass them, just for reference) and displayed to the attacker.

\begin{figure}
 \centering
    \includegraphics[width=0.5\textwidth]{./pic/patches.jpg}
    \caption{Illustration of overlapping patches the network process photos.}
    \label{fig-patches}
\end{figure}

\end{enumerate}

These steps are repeatedly executed to enable the attacker to monitor the victim. The workflow of our system is shown in fig.~\ref{fig-workflow}. The training data for the network is also gathered in this way. Different lenses have different photographing abilities and blurring patterns, so the model has to be trained for each phone with training images captured from it. When using smartphones with optical zoom, the images will shift slightly over time even if we keep them completely still, so the aligning phases are still needed. To reduce calculation and better align the images with the ground truth, we drew a box around the text on the victim's screen, replacing the edges of the phone for alignment and cropping in the alignment step (as shown in fig.~\ref{fig-workflow}), but our system works perfectly without it.
\begin{figure}
 \centering
    \includegraphics[width=0.5\textwidth]{./pic/workflow.pdf}
    \caption{Illustration of the workflow of our shoulder-surfing system.}
    \label{fig-workflow}
\end{figure}

### 2020-06-21 evaluation.tex
add eval

\section{Model Evaluation}
We evaluate the ability of the network model, testing its performance in different training and testing conditions.
\subsection{Performance In Controlled Environment}
We train and test the model with the images captured with exactly the same environment parameters, and used Peak Signal to Noise Ratio to evaluate the accuracy of the recovered images(see Table~\ref{table-control}). Moreover, the ultimate goal of our system is the readability of the recovered images, so we also used Optical Character Recognition(OCR) services to evaluate the accuracy. On average the model achieves 96.5\% OCR accuracy. Considering the complexity of Chinese characters, and the assist of context when read by a human being, we believe this result proves that this model is highly functional when ignoring the environmental parameters.

@@

\subsection{Performance In Random Environment}
We train the model with data captured in different environments, as mentioned before, and test its ability in other environments(see Table~\ref{table-random}). The model achieves 93.5\% accuracy.

\begin{table}  
\begin{tabular}{c|c|c|c|c} 
Environment & Day,1.4m & Day,1.8m & Night,1.4m & Night,1.8m \\ \hline
PSNR(db) & 13.32 & 11.17 & 9.744 & 9.558 \\ \hline
OCR Accuracy(\%) & 100 & 97 & 92 & 85 \\
\end{tabular} 
\caption{Performance in Random Environment}
\label{table-random}
\end{table}

We compare the results to discover the influence of the surrounding environment: The model performs best in daytime and weaker illumination may decrease its ability. Also, the model performs better at closer distances, but this difference is trivial.

\subsection{Adapting Ability}
We train the model with fewer groups of data, exposing it to fewer variations of environment parameters, and examine the model’s performance in other environments. The results are shown in Table~\ref{table-adapt}.

@@

\subsection{Comparison with other architectures}
We train and test other commonly used architectures with the same sets of data and evaluate their results. We chose SRCNN, a commonly used single image SR network, and applied it to each single image before merging the results by pixel-level averageing. We also used a multi-frame version of CNN consisting of 3D convolutional layers, designed for video super resolution(VideoSR). However, as mentioned above, it is very difficult for the single image approaches to utilize information and distinguish the noized and deformed patterns, while VideoSR approaches rely apon consistency between frames, so they fail to give satisfactory results. We used the relatively easys 'daytime 1.2m-distance direct' group of data for testing. The results are shown in Table~\ref{table-comp}.

@@

\section{System Evaluation}
\subsection{Accuracy}
We build the system on smartphone and evaluate its performance in real-life environments. We experiment with a Redmi 6A smartphone (with a camera of 13 million pixels) for the attacker and a HUAWEI Mate8 smartphone for the victim. We ask 5 human participants to read the reconstructed characters to evaluate the usability of our model. No participants can read the unprocessed images, but all of them can decipher the information on the reconstructed image without much difficulty. The results are shown in Table~\ref{table-accuracy}.

>>>>

 
\section{Model Evaluation}
We evaluate the ability of the network model, testing its performance in different training and testing conditions. We perform the following experiments with two phones: a Redmi 6A smartphone, with a single rear camera with 13 million pixels and digital zoom only, and a HUAWEI P40 Pro, with multiple rear cameras, the telephoto camera(which we use in the experiments) possessing up to 5x optical zooming ability which we will utilize fully in our experiments. 
\subsection{Performance In Controlled Environment}
We train and test the model with the images captured with exactly the same environment parameters, and used Peak Signal to Noise Ratio to evaluate the accuracy of the recovered images(see Table~\ref{table-control} and Fig.~\ref{fig-control}). Moreover, the ultimate goal of our system is the readability of the recovered images, so we also used Optical Character Recognition(OCR) services to evaluate the accuracy. The model with traditional lenses(without optical zoom) is trained and tested at 1~2 meters range, while the one with optical zoom at 5~7.5 meters, at which distance less than 5\% of the characters(only the simplist ones) can be recognized by humans from the photos without the assistance of SR algorithms. The model can achieve an accuracy above 90\% at 1.8m with traditional lenses and 6m with optical zooming lenses. Considering the complexity of Chinese characters, and the assist of context when read by an OCR recognizer, we believe this level of accuracy can provide sufficient data at a shoulder surfing scenario, thus proving the efficiency of our model.
In the optical zoom group the accuracy of the model dropped drastically at 7m distance. Increased distances means less data and less restrictions of the possible outputs, which leads to artifacts(missing or misplaced strokes,etc.). It's the nature of Chinese characters that one mistaken stroke will largely affect its readability, leading to the result that while the pixelwize error rises steadily with the increased distance, the accuracy will experience a drastic drop.

@@

\begin{figure}
 \centering
    \includegraphics[width=0.5\textwidth]{./pic/distance.pdf}
    \caption{Performance in Controlled Environment(optical zoom lenses)}
    \label{fig-control}
\end{figure}
\subsection{Performance In Random Environment}
We train the model with data captured in different environments, as mentioned before, and test its ability in other environments(see Table~\ref{table-random} and Fig.~\ref{fig-random}). The model achieves an accuracy above 90\% at 1.8m with traditional lenses and 6m with optical zooming lenses.

\begin{table}  
\begin{tabular}{c|c|c|c|c} 
Environment & Day,1.4m & Day,1.8m & Night,1.4m & Night,1.8m \\ \hline
PSNR(db) & 13.32 & 11.17 & 9.744 & 9.558 \\ \hline
OCR Accuracy(\%) & 100 & 97 & 92 & 85 \\
\end{tabular} 
\caption{Performance in Random Environment(traditional lenses)}
\label{table-random}
\end{table}

\begin{figure}
 \centering
    \includegraphics[width=0.5\textwidth]{./pic/distance2.pdf}
    \caption{Performance in Random Environment(optical zoom lenses)}
    \label{fig-random}
\end{figure}
We compare the results to discover the influence of the surrounding environment: The model performs best in daytime and weaker illumination may decrease its ability. Also, the model performs better at closer distances. As the model is trained initially on the 5m group data, it performs expecially well at this distance, while the accuracy at other distances experience certain levels of decrease. Also, similar to the experiments at controlled environments, random artifacts start to encompass OCR compensation, rendering the result images highly unreadable, until at 7.5m distance only the simplist characters can escape from being flooded by noize.

\subsection{Adapting Ability}
We train the model with fewer groups of data, exposing it to fewer variations of environment parameters, and examine the model’s performance in other environments. The results are shown in Table~\ref{table-adapt}.Only the results from the traditional lenses is shown, as the optical zoom lenses group face longer distances and more complex distortions, and with incomplete data the model fails to manage any reasonable reconstruction on the test dataset, resulting in extremely low accuracy in all experiments.

@@

\subsection{Comparison with other architectures}
We train and test other commonly used architectures with the same sets of data and evaluate their results. We chose SRCNN, a commonly used single image SR network, and applied it to each single image before merging the results by pixel-level averageing. We also used a multi-frame version of CNN consisting of 3D convolutional layers, designed for video super resolution(VideoSR). However, as mentioned above, it is very difficult for the single image approaches to utilize information and distinguish the noized and deformed patterns, while VideoSR approaches rely apon consistency between frames, so they fail to give satisfactory results. We used the relatively easy 'daytime 1.2m-distance direct with traditional lenses' group of data for testing. The results are shown in Table~\ref{table-comp}.

@@

\section{System Evaluation}
\subsection{Accuracy}
We build the system on smartphone and evaluate its performance in real-life environments. We experiment with a Redmi 6A smartphone (with a camera of 13 million pixels) for the attacker and a HUAWEI Mate8 smartphone for the victim. As the telephoto cameras can assist the attacker to see clearly at approximately 3m distance without any aid from SR algorithms, we believe it's insignificant to further extend this distance to judge it as a threat to privacy, so that the following experiments are performed with traditional lenses at 1~2m range. We ask 5 human participants to read the reconstructed characters to evaluate the usability of our model. No participants can read the unprocessed images, but all of them can decipher the information on the reconstructed image without much difficulty. The results are shown in Table~\ref{table-accuracy}.

### 2020-06-21 implementation.tex
add eval

As a result of these observations, we have to collect images in varied environments. Our experiment consists of 2 smartphones at a distance between 1 and 2 meters, one for the attacker and one the victim. An app runs inside the attacker's phone, taking photos continuously, adjusting its focus and aperture, trying it's best to capture high-quality photos. Another app runs inside the victim's phone, displaying random characters with several fonts and colors, for the attacker to capture. The characters are selected from commonly used Chinese characters with 5 to 10 strokes and the English alphabet, and we divide this assemble into training and testing subsets. As the English characters are apparently easier to classify and reconstruct for the networks, the experiments testing the performance of the network will be performed only on Chinese characters, but it is our observation that our system works on English characters as well as Chinese characters. As the experiment goes on, the attacker phone will keep on taking photos in burst mode (20 photos per time), and the victim phone will change the characters it is displaying at a fixed interval, when approximately 100 images were taken by the attacker. We change the environmental setting whenever about 2k photos were taken, relocating the phones (while keeping their distance between 1 and 2 meters) or modifying the angle of the phones. The attacker will always point its phone directly at the victim, keeping its screen in the middle of the photos; The victim, however, may tilt its phone at an angle within 30 degrees. We then readjust the focus and aperture of the attacker's phone to maximize the image quality before continuing data collection. Screenshots were taken in the victim's phone each time it changes its display, and these screenshots are scaled, spun and deformed according to the distance and angle between the phones at the time, and used as ground truth for training and evaluation.

>>>>

As a result of these observations, we have to collect images in varied environments. Our experiment consists of 2 smartphones, one for the attacker and one the victim. Their distance is between 1 and 2 meters for traditional lenses(for the camera of the attacker's phone) without optical zooming, and 5 to 7.5 meters for lenses with optical zooming. Both phones are fixed to stands to keep them completely still, but as mentioned above, the lenses with optical zoom will shift slightly time to time, which is similar to a handheld situation. An app runs inside the attacker's phone, taking photos continuously, adjusting its focus and aperture, trying it's best to capture high-quality photos. Another app runs inside the victim's phone, displaying random characters with several fonts and colors, for the attacker to capture. The characters are selected from commonly used Chinese characters with 5 to 10 strokes and the English alphabet, and we divide this assemble into training and testing subsets. As the English characters are apparently easier to classify and reconstruct for the networks, the experiments testing the performance of the network will be performed only on Chinese characters, but it is our observation that our system works on English characters as well as Chinese characters. As the experiment goes on, the attacker phone will keep on taking photos in burst mode (20 photos per time), and the victim phone will change the characters it is displaying at a fixed interval, when approximately 100 images were taken by the attacker. We change the environmental setting whenever about 2k photos were taken, relocating the phones (while keeping their distance between 1 and 2 meters) or modifying the angle of the phones. The attacker will always point its phone directly at the victim, keeping its screen in the middle of the photos; The victim, however, may tilt its phone at an angle within 30 degrees. We then readjust the focus and aperture of the attacker's phone to maximize the image quality before continuing data collection. Screenshots were taken in the victim's phone each time it changes its display, and these screenshots are scaled, spun and deformed according to the distance and angle between the phones at the time, and used as ground truth for training and evaluation.
